Novakovic et al 2019 reanalysis

### 2024-01-03 figs/ART_novakovic.Rmd
art simplification
art fix

baseDir <- "."
sample_metadata <- pData(phenoData(gse))
targets <- sample_metadata

files <- list.files(WORKING_DIR,pattern = "GSM",recursive = TRUE)
mybase <- unique(gsub("_Red.idat.gz" ,"", gsub("_Grn.idat.gz", "" ,files)))
mybase <- paste(WORKING_DIR,"/",mybase,sep="")
targets$Basename <- mybase
head(targets)

# filter time of birth as were not interested in follow up samples
targets <- subset(targets,`time of collection:ch1`=="birth")
rgSet <- read.metharray.exp(targets = targets)
rgSet

@@

write.table(top_GIFT_vs_FX$dma,file="novakovic_top_GIFT_vs_FX.tsv",sep="\t",quote=FALSE)

@@

write.table(top_nat_vs_ART$dma,file="novakovic_top_nat_vs_ART.tsv",sep="\t",quote=FALSE)

>>>>

baseDir <- "."
sample_metadata <- pData(phenoData(gse))
targets <- sample_metadata
targets <- subset(targets,`time of collection:ch1`=="birth")
targets$Basename <- head( gsub("_Grn.idat.gz","",list.files("IDAT",full.names=TRUE,pattern="Grn")) , 207 )
head(targets)

rgSet <- read.metharray.exp(targets = targets)
rgSet

@@

@@
